Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-11 paper.qmd
Corrected grammar

The tSNE behaviour is to squeeze the low density area of the data together into the layout. This is common in other NLDR methods also, which means analysts needs to be aware the if their data is not sampled relatively uniformly apparent closeness in the \gD{} may correspond to sparseness in \pD{}.

>>>>

The tSNE behaviour is to squeeze the low density area of the data together into the layout. This is common in other NLDR methods also, which means analysts need to be aware that if their data is not sampled relatively uniformly, apparent closeness in the \gD{} may correspond to sparseness in \pD{}.
